Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-03-14 docs/ms.tex
Update ms.tex

\subsection{Likelihood Function}

@@

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropic
of Universe ,we expect $\phi$ has a uniform distribution from 0 to
$\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

@@

If there is measurement error on $\epsilon_{ob}$,we will have 
\begin{equation}
L(\vec{g},\alpha|\epsilon_{ob})=p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})p(\epsilon_{\ell}|\vec{g},\alpha)
\end{equation}
Here the prior distribtuion we use for $\vec{g}$ is a 2Dflat distribution
in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

The prior of $\alpha$ some how depends on the model we choose for
intrinsic ellipticity distribution .When we use the step function
model for P($\epsilon_{0}$),we find that we need to use a prior on
$\alpha$ .
\begin{equation}
Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

@@

While making the posterior samples we choose to use the classical
Gibbs sampler.

>>>>

\subsection{Likelihood Functions}

@@

and it's inverse formula 
\begin{equation}
\epsilon_{0}=\frac{\epsilon_{\ell}-g}{1-g^{*}\epsilon_{\ell}}
\end{equation}
from Schramm \& Kayser (1995), Seitz \& Schneider (1997), where $\epsilon$
is represented as a complex variable and g, $g^{*}$ are the reduced
shear and its complex conjugate, respectively. $\epsilon$ is defined
in terms of the major and minor axes and orientation a, b, $\phi$,
respectively, as $\epsilon$ = (a − b)/(a + b) exp(2i$\phi$). Due to the isotropicity
of Universe ,we expect $\phi$ has a uniform distribution from 0 to
$\pi$.Then we can expect 
\begin{equation}
<\epsilon_{\ell}>=g
\end{equation}

@@

If there is measurement error on $\epsilon_{ob}$,we will have 
\begin{equation}
L(\vec{g},\alpha|\epsilon_{ob})=p(\epsilon_{ob}|\vec{g},\alpha)=\int f(\epsilon_{ob}|\epsilon_{\ell})p(\epsilon_{\ell}|\vec{g},\alpha)
\end{equation}
Here the prior distribtuion we use for $\vec{g}$ is a 2D flat distribution
in the region $|g|<1$.Therefore $prior(\vec{g)}=\begin{cases}
1 & |\vec{g}|<1\\
0 & |\vec{g}|>1
\end{cases}$

The prior of $\alpha$ some how depends on the model we choose for
intrinsic ellipticity distribution .When we use the step function
model for P($\epsilon_{0}$),which we'll decribe latter.We find that
we need to use a prior on $\alpha$ .
\begin{equation}
Prior(\vec{\alpha}|\xi)=exp(-\xi\sum(\alpha_{i}-\alpha_{i-1})^{2})
\end{equation}

@@

While making the posterior samples $p(\g,\alpha|Data) we choose to use the classical
Gibbs sampler.
